Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System

### 2022-12-20 paper/paper.tex
Add Authors

At the beginning, the task allocation block will assign the agents in $team_i$ with some search tasks in $area_i$ to build the occupancy map and find targets. The search task is assumed to be allocated by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks in Fig. \ref{fig:S_task} as a set $task_1=\{ T_j | j=1,2,...,5 \}\cup\{T_6\}$, then the proper agent-task pairs $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}\cup\{(\alpha_{i+1,2},T_6)\}$ can be obtained through the task allocation block. Suppose a goal is found after a while as shown in Fig. \ref{fig:S_task}. At this point, we have a rescue task $T_7$. The new task list $task_2=task_1\cup\{ T_7 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{i,5}$ and $\alpha_{i+1,2}$ to perform $T_7$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{i,5},T_5),(\alpha_{i+1,2},T_6) \})\cup\{ (\alpha_{i,5},T_7),(\alpha_{i+1,2},T_7) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/SR_area.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $team_i$ is responsible for $area_i$.}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/S_task.png}\caption{The allocation of search tasks in the $i$th team and $(i+1)$th team at the begining. The search tasks $T_j,j=1,2,...,6$ are allocated by the task allocation block. The content of the search tasks is to reach some consecutive goals $q_{goal}$ (black dots in figure) so that the straight path between goals $q_{goal}$ can cover the unsearched area. For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}. For robots, $q_{goal}$ will be passed to path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
    \label{fig:S_task}
\end{figure}

@@

\section{conclusion}
In this study, a system architecture of reference trajectory planning and tracking control of hybrid URTS for S\&R usage is given. This gives a holistic view of the operational framework of how to integrate motion planning and robust decentralized fault-tolerant tracking control for hybrid URTS. By decomposing the path planning process into three subprocess, i.e., path planning, behavior layer, local motion planning, some common roadmap-based path planning algorithm can be applied in URTS. Next, we focus on the local motion planning of UAV flying and robot walking behavior. Besides, the bridging method between the reference path planned by the local motion planning block and the reference trajectory to be  followed in the reference tracking control block is also given. By a general nonlinear agent dynamics model, the tracking control problem of UAV and robot can be analyzed together. Through a feedforward control strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals. Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic system. After that, a robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for each agent in the hybrid URTS. To solve the robust $H_\infty$ decentralized observer-based feedforward FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox. A simulation example is given to illustrate more concretely how the proposed hybrid URTS architecture actually works. Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward FTC method is also verified by the simulation results. In the future, we will...

@@

>>>>

At the beginning, the task allocation block will assign the agents in $team_i$ with some search tasks in $area_i$ to build the occupancy map and find targets. The search task is assumed to be allocated by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks in Fig. \ref{fig:S_task} as a set $task_1=\{ T_j | j=1,2,...,5 \}\cup\{T_6\}$, then the proper agent-task pairs $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}\cup\{(\alpha_{i+1,2},T_6)\}$ can be obtained through the task allocation block. Suppose a goal is found after a while as shown in Fig. \ref{fig:S_task}. At this point, we have a rescue task $T_7$. The new task list $task_2=task_1\cup\{ T_7 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{i,5}$ and $\alpha_{i+1,2}$ to perform $T_7$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{i,5},T_5),(\alpha_{i+1,2},T_6) \})\cup\{ (\alpha_{i,5},T_7),(\alpha_{i+1,2},T_7) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/SR_area.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $team_i$ is responsible for $area_i$.}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.105]{fig/S_task.png}\caption{The allocation of search tasks in the $i$th team and $(i+1)$th team at the begining. The search tasks $T_j,j=1,2,...,6$ are allocated by the task allocation block. The content of the search tasks is to reach some consecutive goals $q_{goal}$ (black dots in figure) so that the straight path between goals $q_{goal}$ can cover the unsearched area. For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}. For robots, $q_{goal}$ will be passed to path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
    \label{fig:S_task}
\end{figure}

@@

\section{conclusion}
In this study, a system architecture of task allocation, reference trajectory planning and tracking control of hybrid URTS for S\&R usage is given. This gives a holistic view of the operational framework of how to integrate motion planning and robust decentralized fault-tolerant tracking control for hybrid URTS. By decomposing the path planning process into three subprocess, i.e., path planning, behavior layer, local motion planning, some common roadmap-based path planning algorithm can be applied in URTS. Next, we focus on the local motion planning of UAV flying and robot walking behavior. Besides, the bridging method between the reference path planned by the local motion planning block and the reference trajectory to be followed in the reference tracking control block is also given. By a general nonlinear agent dynamics model, the tracking control problem of UAV and robot can be analyzed together. Through a feedforward control strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals. Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic system. After that, a robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for each agent in the hybrid URTS. To solve the robust $H_\infty$ decentralized observer-based feedforward FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox. A simulation example is given to illustrate more concretely how the proposed hybrid URTS architecture actually works. Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward FTC method is also verified by the simulation results.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author1.jpg}}]{Bor-sen chen}
    (Life Fellow, IEEE) received the B.S. degree in electrical engineering from the Tatung Institute of Technology, Taipei, Taiwan, in 1970, the M.S. degree in geophysics from National Central University, Chungli, Taiwan, in 1973, and the Ph.D. degree in electrical engineering from the University of Southern California, Los Angeles, CA, USA, in 1982. He was a Lecturer, an Associate Professor, and a Professor with the Tatung Institute of Technology, from 1973 to 1987. He is currently the Tsing Hua Distinguished Chair Professor of electrical engineering and computer science with National Tsing Hua University, Hsinchu, Taiwan. His current research interests include control engineering, signal processing, and systems biology. He has received the Distinguished Research Award from the National Science Council of Taiwan four times. He is also the National Chair Professor of the Ministry of Education of Taiwan.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author2.jpg}}]{Ting-Wei Hung}
    received the B.S. degree in the department of engineering science from the National Cheng Kung University, Tainan, Taiwan, in 2020, and the M.S. degree from the Department of Electrical Engineering, National Tsing Hua University, in 2022. His current research interests include robotics, robust control, and team formation control.
\end{IEEEbiography}
